### 2013-04-03 doc/final_report/design.tex
Some spelling mistakes dealt with

Despite the use of an iterative development methodology, some of the key
components within Partridge were designed up front in order to accelerate
implementation and reduce time overheads when adding new components to the
system. The components that make up Partridge and the ways in which they react
are described and analysed below. Choices regarding the type of application,
the target audience and the programming environment are also discussed.

@@

It was decided from the outset that Partridge would be a web-based tool.
Web-based systems can generally be run on any computer with access to the
internet and a modern web browser. This also means that there is no need for
the end user to install or configure extra software on their computers, making
Partridge accessible to non-technical users and those who have aggressive
software restrictions on their computers, such as GPs and users of public
computers in libraries or on academic sites.

In order to function as a website, Partridge needed to be developed as a server
application that produced Hyper Text Markup Language (HTML) output that a web
browser could interpret and display. The browser rendering the forms must then
communicate with a backend system capable of querying and returning papers to
the user based on their input. This lead to the decision to split development
of Partridge into two core components: the Web Frontend comprising of user
interface elements and presentation logic and the Web Backend comprising of
intelligent systems to classify, filter and query papers using some of the NLP
techniques discussed previously.

One of the main requirements for a web server is that it responds to requests
relatively quickly, ideally within 10 seconds or less. If the response is any
slower than this, the user may get impatient and give up trying to use the
system, or in some cases, their web browser may timeout and stop trying to load
the page. Many of the processes involved in extracting meaningful CoreSC
information from papers are very slow. This means that processing papers
during web requests is not really feasible, since it may take several minutes
for a single paper to be annotated and classified. Therefore, a third core
component was identified: a paper preprocessor service that runs on the server
and converts, annotates and classifies papers as soon as they are uploaded.

@@

Rather than building a web server from the ground up, most modern web
applications are written in higher level languages that run on top of standard,
open source web servers such as Apache or nginx. Common language choices
include PHP, Python, Perl and Java, all of these languages supported by large
communities of developers and users who provide with excellent documentation
and support if required.  For the implementation of Partridge, Python was
selected as the programming language of choice. This was partially due to the
author's familiarity with the language and also due to the availability of
stable data mining\cite{curk05} and natural language
processing\cite{bird2009natural} libraries for the Python programming
environment. Python is an interpreted cross-platform language, minimising
deployment problems and supports natively compiled C and C++ extension
libraries allowing intensive processing  and number crunching to be offloaded
to native plugins, increasing application processing speed.

@@

The Web Frontend for the system would need to be written using a combination of
HTML markup and JavaScript. HTML is not a programming language in itself and
doesn't contain any logic. It is merely a code representation of the interface
to be rendered in the browser window which is interpreted once it has been
downloaded from the web server. In order to carry out actions on the HTML such
as validating user input and manipulating parts of the display, JavaScript is
also downloaded from the web server and interpreted by the browser. Although
this requires the developer to have knowledge of two extra technologies on top
of Python, it also makes enforcing the design principle of keeping presentation
and logic separate a lot easier.

Due to the large number of popular web browsers on the market, implementing
JavaScript in a slightly different way, Javascript can be very difficult to
write in a cross-browser compatible way. To maximise compatibility and reduce
development time, it was decided jQuery would be used in developing the
JavaScript frontend behaviours. jQuery is a library of utility functions
designed for manipulating HTML documents in a uniform way across all compatible
browsers \cite{jquery2013}. As of February 2013, it is estimated that Chrome and
Firefox are currently the most popular web browsers, holding 50\% and 29.6\% of
the market share respectively\cite{browserstats2013}. Internet Explorer is the
third most popular browser. However, there are several well known compatibility
issues with Internet Explorer, Microsoft themselves condemning version 6.0 of
their browser\cite{ie6death}. For this reason, it was decided that Partridge
would only support Firefox and Chrome. A working interface in modern editions
of the Internet Explorer family of browsers would be a bonus.  However, no time
was allocated to ensuring compatibility of Partridge with Internet Explorer.

@@

Figure \ref{fig:high_level_components} shows a very high level description of
the system's three main components, the database server and the ways that they
communicate. Communication between the Web Interface and the other two
components is carried out via HTTP requests to the underlying Apache server.
Communication between the web backend and the paper preprocessor is implicit
via the data storage system. Direct communication between these components is
redundant since the web backend cannot gain any extra information from the
paper preprocessor while a paper is still being analysed and all finished
papers are added to the database which the web backend has full access to
anyway.

@@

The final stage in the preprocessor pipeline is paper classification. During
this stage, features wil be extracted from the papers and used to classify the
paper in three different ways. The paper's type: case study or review paper
etc. will be determined using the presence or absence of different CoreSC labels
within the paper and their relative proportions. The subject of paper will be
determined by the presence of domain specific nouns and adjectives within the
paper. For example, a biology paper might contain words such as enzyme or amino
acid. The result of the paper, i.e. whether the paper was conclusive and if the
results were positive or negative, will be detected through the presence or absense
of words with a strong sentiment polarity as discussed by Wilson et al
(2005)\cite{Wilson05Polarity}. The results from the whole process are then
passed into the data store and saved.

@@

\subsection{ Data Storage }
\label{sec:db_layout}
It is expected that a given Partridge instance may grow in size to contain
tens of thousands of individual papers that have been annotated and are available to
the web backend for inclusion into a user's search results. Reading in and
parsing each individual XML file stored in the system is not really feasible
when handling a HTTP request from the web frontend, this sort of process would
take a long time to execute. To provide fast search and retrieval of paper
data, a Relational Database Management server (RDBMS) was chosen for storage of
papers that have been preprocessed using the system described above. An
overview of the database schema is illustrated in Figure \ref{fig:e-r-diagram}.

@@

Partridge's database is required to keep track of all of the papers that have
been added to the system. The Paper entity represents a single paper stored in
Partridge. Information extracted by the classifiers such as the paper's type,
topic and result are stored as part of the main paper entity. The title and
topic are also stored for easy retrieval. One of the key requirements of
Partridge is querying within a CoreSC field of a paper. Therefore, all
sentences are stored as entities along with their CoreSC annotation. The sentence
text is an index field to facilitate fast recall from the database.

It is probable that any given author may have contributed to multiple papers
stored within the system.  Therefore authors are treated as entities within the
RDBMS and the many to many relationship between papers and authors is
facilitated using the intermediary table PaperAuthors. A PaperAuthor record
contains a boolean field used to indicate whether an author linked to a
specific paper was the primary author on that paper.

@@

The Flask web framework uses a model view controller-like architecture. Each
behaviour of the server: handling paper uploads, displaying paper query
results, allowing users to download papers, can be considered a `view'. Views
register themselves with Flask under a specific URL. When Flask receives a
request to any such URL, it automatically routes the request through to the
View object\cite{flask2012}.

@@

The search or `Keywords' section of the form shows a set of controls for
specifying terms that must appear within sections of a document for it to show
up in the search results. The user enters a search term in the input box on the
top right of the form and then selects which section of the paper the term
should appear within. This could be any of the CoreSC labels within the paper or
within the abstract. The user could also specify a specific author's name. Once
they are happy with their keywords and section, they click ``Add" and the
keyword/section pair are inserted into the table on the bottom right. If they
wish to remove a query constraint from this table, they can select it and click
the ``Delete" button.

Once the user is happy with their search, they can click the ``Search" button
at the extreme top right of the form to carry out the query and see the
results.

@@

Once a user has made their query, the results are displayed for them to peruse
and find relevant papers to read. Figure \ref{fig:results_mockup} shows a
mockup of the results view. This simplistic page lists all of the papers found
during the query in relevence order. The results are paginated so that the user
does not have to wait for a large page to render. It is hoped that users will
run specific queries that do not return a high number of results. There is a
prominent link at the top of the page that allows the user to go back to the
query form and amend their query if the results are not satisfactory.

@@

The paper's title and author are displayed prominently in the top left hand
corner of the page. The full abstract text is shown so that the user can read
it and determine the paper's relevance to them. There is also a graph showing
each of the CoreSC types and proportion within the paper (the example chart only
shows three CoreSC label types for brevity). If the user is
interested in the paper, they can click the Download link at the top of the
page to access the annotated XML file stored in the system.

\subsubsection{Paper Upload Form}
Paper uploading is another highly important user activity within Partridge.
Without users uploading papers, Partridge has no data to work with. It was
therefore, very important to make paper uploading as simplistic as possible to
the end user. Figure \ref{fig:paper_upload} shows Partridge's main paper upload
form.

>>>>

Despite the use of an iterative development methodology, some of the key
components within Partridge were designed 'up front' in order to accelerate
implementation and reduce the time needed to add new components to the
system. The components that make up Partridge and the ways in which they react
are described and analysed below; choices regarding the type of application,
the target audience and the programming environment are also discussed.

@@

From the outset, the aim was that Partridge would be a web-based tool.
Web-based systems can generally be run on any computer with access to the
internet and a modern web browser. This also means that there is no need for
the end user to install or configure extra software on their computers, making
Partridge accessible to non-technical users and those who have aggressive
software restrictions on their computers, such as GPs and the users of public
computers in libraries or on academic sites.

In order to function as a website, Partridge needed to be developed as a server
application that produced Hyper Text Markup Language (HTML) output with which a web
browser could interpret and display. The browser rendering the forms must then
communicate with a backend system capable of querying and returning papers to
the user based on their input. This lead to the decision to split the development
of Partridge into two core components: the Web Frontend comprising of user
interface elements and presentation logic and the Web Backend comprising of
intelligent systems to classify, filter and query papers using some of the NLP
techniques discussed previously.

One of the main requirements for a web server is that it responds to requests
relatively quickly, ideally within 10 seconds or less. If the response is any
slower than this, the user may get impatient and give up trying to use the
system, or in some cases, their web browser may timeout and stop trying to load
the page. Unfortunately, many of the processes involved in extracting meaningful CoreSC
information from papers are very slow. This means that processing papers
during web requests is not really feasible, since it may take several minutes
for a single paper to be annotated and classified. Therefore, a third core
component was identified: a paper preprocessor service that runs on the server
and converts, annotates and classifies papers as soon as they are uploaded.

@@

Rather than building a web server from the ground up, most modern web
applications are written in higher level languages that run on top of standard,
open source web servers such as Apache or nginx. Common language choices
include PHP, Python, Perl and Java; all of these languages are supported by large
communities of developers and users who provide with excellent documentation
and support if required.  Python was
selected to implement Partidge. This was partially due to the
author's familiarity with the language and also due to the availability of
stable data mining\cite{curk05} and natural language
processing\cite{bird2009natural} libraries for the Python programming
environment. Python is an interpreted cross-platform language, minimising
deployment problems and supports natively-compiled C and C++ extension
libraries allowing intensive processing  and number crunching to be offloaded
to native plugins, increasing application processing speed.

@@

The Web Frontend for the system had to be written using a combination of
HTML markup and JavaScript. HTML is not a programming language in itself and
doesn't contain any logic. It is merely a code representation of the interface
to be rendered in the browser window which is interpreted once it has been
downloaded from the web server. In order to carry out actions on the HTML such
as validating user input and manipulating parts of the display, JavaScript is
also downloaded from the web server and interpreted by the browser. Although
this requires the developer to have knowledge of two extra technologies in addition to Python, it also makes enforcing the design principle of keeping presentation
and logic separate a lot easier.

Due to the large number of popular web browsers on the market, implementing
JavaScript in a slightly different way, Javascript can be very difficult to
write in a cross-browser compatible way. To maximise compatibility and reduce
development time, it was decided that jQuery would be used in developing the
JavaScript frontend behaviours. jQuery is a library of utility functions
designed for manipulating HTML documents in a uniform way across all compatible
browsers \cite{jquery2013}. As of February 2013, it is estimated that Chrome and
Firefox are currently the most popular web browsers, holding 50\% and 29.6\% of
the market share respectively\cite{browserstats2013}. Internet Explorer is the
third most popular browser. However, there are several well-known compatibility
issues with Internet Explorer, Microsoft themselves condemning version 6.0\cite{ie6death}. For this reason, it was decided that Partridge
would initially only support Firefox and Chrome; a working interface in modern editions
of the Internet Explorer family of browsers would be a bonus.  However, no time
was allocated to ensuring compatibility of Partridge with Internet Explorer.

@@

Figure \ref{fig:high_level_components} shows a very high level description of
the system's three main components, the database server and the ways that they
communicate. Communication between the Web Interface and the other two
components is carried out via HTTP requests to the underlying Apache server.
Communication between the web backend and the paper preprocessor is implicit
via the data storage system. Direct communication between these components is
redundant since the web backend cannot gain any extra information from the
paper preprocessor while a paper is still being analysed. Furthermore, all finished
papers are added to the database which the web backend has full access to
anyway.

@@

The final stage in the preprocessor pipeline is paper classification. During
this stage, features wil be extracted from the papers and used to classify the
paper in three different ways. The paper's type: case study or review paper
etc. will be determined using the presence or absence of different CoreSC labels
within the paper and their relative proportions. The subject of paper will be
determined by the presence of domain specific nouns and adjectives within the
paper. For example, a biology paper might contain words such as 'enzyme' or 'amino
acid.' The result of the paper, i.e. whether the paper was conclusive and if the
results were positive or negative, will be detected through the presence or absence
of words with a strong sentiment polarity as discussed by Wilson et al
(2005)\cite{Wilson05Polarity}. The results from the whole process are then
passed into the data store and saved.

@@

\subsection{ Data Storage }
\label{sec:db_layout}
It is expected that Partridge may grow in size to contain
tens of thousands of individual papers that have been annotated and are available to
the web backend for inclusion into a user's search results. Reading and
parsing each individual XML file stored in the system is not really feasible
when handling a HTTP request from the web frontend, this sort of process would
take a long time to execute. To provide fast search and retrieval of paper
data, a Relational Database Management server (RDBMS) was chosen for storage of
papers that have been preprocessed using the system described above. An
overview of the database schema is illustrated in Figure \ref{fig:e-r-diagram}.

@@

Partridge's database is required to keep track of all of the papers that have
been added to the system. The Paper entity represents a single paper stored in
Partridge. Information is extracted and classified by indicators such as the paper's type,
topic and resul. This is are stored as part of the main paper entity. The title and
topic are also stored for easy retrieval. One of the key requirements of
Partridge is querying within a CoreSC field of a paper. Therefore, all
sentences are stored as entities along with their CoreSC annotation. The sentence
text is an index field to facilitate fast recall from the database.

It is probable that any given author may have contributed to multiple papers
stored within the system.  Therefore authors are treated as entities within the
RDBMS and the many to many relationship between papers and authors is
facilitated using the intermediary table PaperAuthors. A PaperAuthor record
contains a boolean field used to indicate whether the author that is linked to a
specific paper was the primary author on that paper.

@@

The Flask web framework uses a model view controller-like architecture. Each
behaviour of the server, handling paper uploads, displaying paper query
results and allowing users to download papers, can be considered a `view'. Views
register themselves with Flask under a specific URL. When Flask receives a
request to any such URL, it automatically routes the request through to the
View object\cite{flask2012}.

@@

The search or `Keywords' section of the form shows a set of controls for
specifying terms that must appear within sections of a document in order to show
up in the search results. The user enters a search term in the input box on the
top right of the form and then selects which section of the paper the term
should appear within. This could be any of the CoreSC labels within the paper or
within the abstract. The user could also specify a specific author's name. Once
they are happy with their keywords and section, they click `Add' and the
keyword/section pair are inserted into the table on the bottom right. If they
wish to remove a query constraint from this table, they can select it and click
the `Delete' button.

Once the user is happy with their search, they can click the `Search' button
at the extreme top right of the form to carry out the query and see the
results.

@@

After the user has made their query, the results are displayed for them
to find relevant papers to read. Figure \ref{fig:results_mockup} shows a
mockup of the results view. This page clearly lists all of the papers found
during the query in order of relevence. The results are paginated so that the user
does not have to wait for a large page to render. It is hoped that users will
run such specific queries that they do not return a high number of results. There is a
prominent link at the top of the page that allows the user to go back to the
query form and amend their query if the results are not satisfactory.

@@

The paper's title and author are displayed prominently in the top left hand
corner of the page. The full text of the abstract is shown so that the user can determine the paper's relevance to them. There is also a graph showing
each of the CoreSC types and proportion within the paper (the example chart only
shows three CoreSC label types for brevity). If the user is
interested in the paper, they can click the Download link at the top of the
page to access the annotated XML file stored in the system.

\subsubsection{Paper Upload Form}
Paper uploading is another very important user activity within Partridge.
Without users uploading papers, Partridge has no data to work with. It was
therefore, very important to make paper uploading as easy as possible to
the end user. Figure \ref{fig:paper_upload} shows Partridge's main paper upload
form.

### 2013-04-03 doc/final_report/evaluation.tex
Some spelling mistakes dealt with

One of the skills that I have honed through my dissertation project this year
has been reflecting communally upon my work with my supervisors. During my work
placement at IBM, I was loosely supervised, however it was never to the close
and exacting standards of Dr Clare and Dr Liakata, whose guidance has 
prevented me from taking several wrong turns during the project. Reflecting
within such a professional community allowed me to develop good professional
praxis and think more deeply about my programming and Partridge as a whole. It
provided an induction into a professional community of academic computer
science and allowed me as a novice to feel comfortable there.

@@

Whilst SAPIENTA is an excellent piece of research in itself and provides
fascinating insights and implications into the makeup of scientific literature,
Dr Liakata concedes that it is purely an experimental system and was not
intended for large scale analysis of batches of papers in the way that it is
utilised by Partridge. During the development of the paper type classifier,
there were several short delays when the SAPIENTA server stopped working and
had to be restarted. It took several weeks to collect enough data for machine
learning for this reason.

@@

During the course of the project, it became clear very quickly that there would
not be time to implement a recommendation engine as originally hoped. Such a
system would need to collect data from users and the papers that they looked at
and correlate it with papers stored in the corpus that the user may be
interested in viewing. Although there wasn't time to build this feature during
the project, I certainly think it is more than feasible.

@@

Partridge already fulfills many of its objectives and has also had a sizeable
impact on the research community. However in its implementation, a number of
topics for further research have also been uncovered.

>>>>

One of the skills that I have honed through my dissertation project this year
has been reflecting communally upon my work with my supervisors. During my work
placement at IBM, I was loosely supervised, however it was never to the close
and exacting standards of Dr Clare and Dr Liakata, whose guidance has 
prevented me from taking several wrong turns during the project. Reflecting
within such a professional community allowed me to develop good professional
praxis and think more deeply about my programming and Partridge as a whole. It
provided an induction into a professional community of academic computer
science and allowed me, as a novice, to feel comfortable there.

@@

Whilst SAPIENTA is an excellent piece of research in itself and provides
fascinating insights and implications into the makeup of scientific literature,
Dr Liakata concedes that it is purely an experimental system and was not
intended for large scale analysis of batches of papers in the way that it is
utilised by Partridge. During the development of the paper type classifier,
there were several short delays when the SAPIENTA server stopped working and
had to be restarted. For this reason, it took several weeks to collect enough data for machine
learning.

@@

During the course of the project, it quickly became clear that there would
not be time to implement a recommendation engine as originally hoped. Such a
system would need to collect data from users and the papers that they looked at
and correlate it with papers stored in the corpus that the user may be
interested in viewing. Although there wasn't time to build this feature during
the project, I certainly think it is more than feasible.

@@

Partridge already fulfills many of its objectives and has also had a sizeable
impact on the research community. However,  during implementation, a number of
topics for further research have also been uncovered.

### 2013-04-03 doc/final_report/implementation.tex
Finished describing the libraries and stuff in appendix
Some spelling mistakes dealt with

\subsection{Format Conversion} Most scientific papers available on the internet
are formatted as PDF documents. However, Partridge uses and stores documents as
XML markup and uses the CoreSC schema by Soldatova and
Liakata\cite{liakata2008guidelines} for annotation. Therefore some spike work
was carried out to determine the feasibility of converting papers published as
PDF documents into XML documents. Townsend \emph{et al.} (2009) liken
converting PDF to XML to ``converting hamburgers into cows," they go on to
explain that PDF documents do not contain any semantic data and documents lose
much of their explicit structure when they are formatted in this way
\cite{Townsend2009}.  Therefore, to convert PDF documents into an NLP-friendly
format, some heuristics must be used to detect the document's
structure\cite{pdfminer}.

@@

\subsection{Annotating with SAPIENTA}

@@

Once a large number of papers had been acquired from ART, PlosOne and PubMed
Central, work could begin on implementing a paper type classifier able to
discriminate between ``Case Study", ``Research" and ``Review" papers. However,
for a machine learning classifier to discriminate between classes of data, it
is necessary to choose a set of features that differ as much as possible
between the classes. For example, to discriminate between cats and dogs,
``number of legs" is a poor feature since both species normally have 4.
However, the noise that these animals make may be a good discriminative feature
since cats tend to mew and dogs bark.

@@

There are several well established features used for classifying text within
the NLP community. However, since Partridge has access to CoreSC annotations
for each paper, an investigation was carried out into how useful CoreSC data
can be as a feature for paper type discrimination. Every sentence in a given
annotated paper has an associated CoreSC label. It is therefore trivial to
calculate the proportion of a paper made up of sentences with a specified
CoreSC type. Several papers were manually inspected and the proportions of each
CoreSC represented within were calculated. A pattern quickly emerged between
the types of paper and the proportions of each CoreSC within them.

@@

All of the papers were manually identified as either a ``Case Study", a
``Review Paper" or a ``Research Paper." They were then loaded into a script and
clustered using their CoreSC respective compositions. K-Means silhouettes were
used as a measure of how effective the clustering process was. This was
repeated for $ K \in [2..8] $ and the best silhouette measurement and value for
K retained. The algorithm consistently showed that K=3 was the best K value.
However, the silhouette value was consistently low. It was suggested that this
may have been because all CoreSC types were considered equally; the less
discriminative CoreSCs may have been offsetting the effect of the highly
discriminative ones.

To remedy this, all papers were again clustered, but using only three CoreSC
labels at a time: reducing the noise from the less important types. The
algorithm was run for all combinations of 3 CoreSC labels, again retaining only
the most successful combination of features and K value based upon the K
silhouette value. This returned a set of much stronger K silhouette values in
general. The algorithm also determined that the combination of ``Background",
``Motivation" and ``Method" CoreSC labels seemed to be the most
discriminative, providing a silhouette value of 0.63.

>>>>

\subsection{Format Conversion} Most scientific papers available on the internet
are formatted as PDF documents. However, Partridge uses and stores documents as
XML markup and uses the CoreSC schema by Soldatova and
Liakata\cite{liakata2008guidelines} for annotation. Therefore some spike work
was carried out to determine the feasibility of converting papers published as
PDF documents into XML documents. Townsend \emph{et al.} (2009) liken
converting PDF to XML to ``converting hamburgers into cows." They go on to
explain that PDF documents do not contain any semantic data and documents lose
much of their explicit structure when they are formatted in this way
\cite{Townsend2009}.  Therefore, to convert PDF documents into an NLP-friendly
format, some heuristics must be used to detect the document's
structure\cite{pdfminer}.

@@

\subsection{Annotating with SAPIENTA}
\label{sec:sapienta_implementation}

@@

Once a large number of papers had been acquired from ART, PlosOne and PubMed
Central, work could begin on implementing a paper type classifier able to
discriminate between `Case Study,' `Research' and `Review' papers. However,
for a machine learning classifier to discriminate between classes of data, it
is necessary to choose a set of features that differ as much as possible
between the classes. For example, to discriminate between cats and dogs,
``number of legs" is a poor feature since both species normally have four.
However, the noise that these animals make may be a good discriminative feature
since cats tend to mew and dogs bark.

@@

There are several well-established features used for classifying text within
the NLP community. However, since Partridge has access to CoreSC annotations
for each paper, an investigation was carried out into how useful CoreSC data
can be as a feature for paper type discrimination. Every sentence in a given
annotated paper has an associated CoreSC label. It is therefore trivial to
calculate the proportion of a paper made up of sentences with a specified
CoreSC type. Several papers were manually inspected and the proportions of each
CoreSC represented within were calculated. A pattern quickly emerged between
the types of paper and the proportions of each CoreSC within them.

@@

All of the papers were manually identified as either a `Case Study,' a
`Review Paper' or a `Research Paper.' They were then loaded into a script and
clustered using their CoreSC respective compositions. K-Means silhouettes were
used as a measure of how effective the clustering process was. This was
repeated for $ K \in [2..8] $ and the best silhouette measurement and value for
K retained. The algorithm consistently showed that K=3 was the best K value.
However, the silhouette value was consistently low. It was suggested that this
may have been because all CoreSC types were considered equally; the less
discriminative CoreSCs may have been offsetting the effect of the highly
discriminative ones.

To remedy this, all papers were again clustered, but using only three CoreSC
labels at a time: reducing the noise from the less important types. The
algorithm was run for all combinations of 3 CoreSC labels, again retaining only
the most successful combination of features and K value based upon the K
silhouette value. This returned a set of much stronger K silhouette values in
general. The algorithm also determined that the combination of `Background,'
`Motivation' and `Method' CoreSC labels seemed to be the most
discriminative, providing a silhouette value of 0.63.

### 2013-04-03 doc/final_report/introduction.tex
Made some changes to design chapter as suggested by Amanda and Maria
Some spelling mistakes dealt with

Since the advent of the 'Digital Age' and the ability of computers to copy and
reproduce information for a negligible cost, the amount of information
available to researchers has been increasing drastically.  B-C Bj\"{o}rk (2009)
estimates that approximately 1.4 Million papers were published in the year 2006
alone\cite{bjork2009}. Moreover, the growing popularity of Open Access
publishing (making papers available to readers for free online\cite{Suber2012})
across most scientific disciplines\cite{bjork2009}\cite{harnad2004comparing} is
providing scientists and researchers with an even larger volume of information
to be processed. As available information increases, relevant material becomes
progressively more difficult to find manually and the need for an automated
information retrieval tool more apparent. The problem is even more vital for
General Practitioners. Goldacre (2008:97) points out that ``there have been an
estimated 15 million medical academic articles published so far, and 5000
journals published every month... picking out what's relevant is a gargantuan
task."\cite{goldacre2008bad}.

@@

\section{Background}

@@

\section{ Literature Review}

@@

Liakata \emph{et al.} (2012) describe a system for automatically processing and
classifying sentences in a research paper according to the scientific concept
they describe (e.g. a sentence can be categorised as a hypothesis, background
information, a method or similar)\cite{citeulike:10444769}. SAPIENTA
(\url{http://www.sapientaproject.com}) is a machine learning application,
trained using a corpus of physical chemistry and biochemistry research papers
that were pre-processed and annotated using Core Information about Scientific
Papers (CISP)\cite{LIAKATA10.644}.

CISP, Soldatova and Liakata (2007), is a way to formally represent core
scientific concepts (CoreSC), e.g. background, hypothesis, method etc., that
should be present in the articles in a logical
ontology\cite{soldatova2007ontology}. Subsequent work implements this set of
concepts as a three layered sentence based annotation scheme (CoreSC scheme)
where annotations are encoded in Extended Markup Language
(XML)\cite{LIAKATA10.644}.

\section{Objectives}

Partridge's main objective is to provide reading recommendations and
information retrieval for scientists and researchers. This should reduce the
amount of extraneous information that users have to read for themselves by
helping them find information specific to their interests more quickly.
Partridge will achieve this through the use of several existing techniques in
Natural Language Processing and utilisation of SAPIENTA as discussed above.

\begin{itemize}
\item The system should provide search within specific CoreSC regions of a given
paper. This would allow users to find the most relevant papers to them. For
example a user may search for "mass spectrometer" within the methodology
section of a paper.
\item Partridge should allow authors and rightsholders of scientific papers to
upload their papers to the system for inclusion into the search system. This
would give Partridge itself more utility and would make involved authors more
accessible.
\item The system should provide filtering of papers based upon their
specific domain (i.e. is the paper primarily concerned with methodology within
an experiment in chemistry or is it about ethics in psychological studies?) and
their result, whether the paper yielded positive, negative or inconclusive
evidence for a hypothesis. 
\item Depending upon the time constraints of the
project, it was hoped that Partridge will also offer a user 'profiling' system
that provides recommendations for researchers based on their reading history.
This feature should help users find relevant papers more quickly or find
research that they may have otherwise overlooked.a
\end{itemize}

>>>>

Since the advent of the 'Digital Age' and the ability of computers to copy and
reproduce information for a negligible cost, the amount of information
available to researchers has been increasing drastically.  B-C Bj\"{o}rk (2009)
estimates that approximately 1.4 Million papers were published in the year 2006
alone\cite{bjork2009}. Moreover, the growing popularity of Open Access
publishing (making papers available to readers for free online\cite{Suber2012})
across most scientific disciplines\cite{bjork2009}\cite{harnad2004comparing} is
providing scientists and researchers with an even larger volume of information
to be processed. As available information increases, relevant material becomes
progressively more difficult to find manually and the need for an automated
information retrieval tool more apparent. The problem is even more vital for
General Practitioners. Goldacre (2008:97) points out that ``...there have been an
estimated 15 million medical academic articles published so far, and 5000
journals published every month... picking out what's relevant is a gargantuan
task."\cite{goldacre2008bad}.

@@

\section{Objectives}
\label{sec:objectives}
Partridge's main objective is to provide reading recommendations and
information retrieval for scientists and researchers. This should reduce the
amount of extraneous information that users have to read for themselves by
helping them to quickly find information specific to their interests.
Partridge will achieve this through the use of several existing techniques in
Natural Language Processing and utilisation of SAPIENTA as discussed above.

\begin{itemize}
\item The system should provide search within specific CoreSC regions of a given
paper. This would allow users to find the most relevant papers to them. For
example, a user may search for "mass spectrometer" within the methodology
section of a paper.
\item Partridge should allow authors and rightsholders of scientific papers to
upload their papers to the system for inclusion into the search system. This
would give Partridge itself more utility and would make involved authors more
accessible.
\item The system should provide filtering of papers based upon their
specific domain (i.e. is the paper primarily concerned with methodology within
an experiment in chemistry or is it about ethics in psychological studies?) and
their results, whether the paper yielded positive, negative or inconclusive
evidence for a hypothesis. 
\item Depending upon the time constraints of the
project, it was hoped that Partridge will also offer a user 'profiling' system
that provides recommendations for researchers based on their reading history.
This feature should help users find relevant papers more quickly or find
research that they may have otherwise overlooked.
\end{itemize}

\section{Background \& Literature Review}

@@

@@

Liakata \emph{et al.} (2012) describe a system for automatically processing and
classifying sentences in a research paper according to the scientific concept
they describe (e.g. a sentence can be categorised as a hypothesis, background
information, a method or similar)\cite{citeulike:10444769}. SAPIENTA
(\url{http://www.sapientaproject.com}) is a machine learning application,
trained using a corpus of physical chemistry and biochemistry research papers
that were manually annotated using the Core Information about Scientific
Papers (CISP)\cite{LIAKATA10.644} schema.

CISP, Soldatova and Liakata (2007), is a way to formally represent core
scientific concepts (CoreSC), e.g. background, hypothesis, method etc., that
should be present in the articles in a logical
ontology\cite{soldatova2007ontology}. Subsequent work implements this set of
concepts as a three layered sentence based annotation scheme (CoreSC scheme)
where annotations are encoded pin Extended Markup Language
(XML)\cite{LIAKATA10.644}.

### 2013-04-03 doc/final_report/methodology.tex
Some spelling mistakes dealt with

Chosing an effective development methodology can play a very large part in the
success or failure of a software project. A number of existing development
methodologies have been developed and used very effectively over the last 50
years. However, custom methodologies are also commonly used for projects that
aren't suited to one of the commonly used approaches. Some common approaches to
software development and the formulation of a custom methodology for Partridge
are discussed below.

@@

As an alternative to the heavyweight Waterfall approach, Beck \emph{et al.}
came up with the principle of the Agile Manifesto, favouring a lightweight,
responsive development model over the heavyweight slow waterfall
system\cite{beck2001agile}. Many of Beck's ideas focus around working in a team
of developers and prioriting communication between team members \emph{(Ibid.)}.
This is most prominent in the Extreme Programming (XP) method of software
development. Since Partridge is an individual project, XP was not really
applicable. However, some concepts like rapid prototyping/spike work and
iterative release cycles were used as part of the Partridge development
methodology.

>>>>

Chosing an effective development methodology is vital to the
success or failure of a software project. A number of existing development
methodologies have been developed and used very effectively over the last 50
years. However, custom methodologies are also commonly used for projects that
aren't suited to one of the commonly used approaches. Some common approaches to
software development and the formulation of a custom methodology for Partridge
are discussed below.

@@

As an alternative to the heavyweight Waterfall approach, Beck \emph{et al.}
came up with the principle of the Agile Manifesto, favouring a lightweight and
responsive development model over the heavyweight, slow waterfall
system\cite{beck2001agile}. Many of Beck's ideas focus around working in a team
of developers and prioriting communication between team members \emph{(Ibid.)}.
This is most prominent in the Extreme Programming (XP) method of software
development. Since Partridge is an individual project, XP was not really
applicable. However, some concepts like rapid prototyping/spike work and
iterative release cycles were used as part of the Partridge development
methodology.

### 2013-04-03 doc/final_report/report.tex
Added a whole load of stuff on testing machine algorithms
Made some crucial changes to the testing chapter and worked in intro and summary
Started writing the implementation chapter
Finished implementation section on clustering and paper type classification
Made some changes to design chapter as suggested by Amanda and Maria
Some spelling mistakes dealt with

\usepackage{fullpage}
\usepackage{pdfpages}
%use the listings package
\usepackage{listings}
%use the English language
\usepackage[english]{babel}
%use graphics
\usepackage{graphicx}
%use wrap figures
\usepackage{wrapfig}
%geometry stuffs
\usepackage{lscape}
%use natbib bibliography package
%\usepackage[numbers]{natbib}
%use harvard bibliography package
%\usepackage{harvard}	
%use captions
\usepackage{caption}
%use multi-row tables
\usepackage{multirow}
\usepackage{url}
\usepackage{subcaption}

@@

I would like to take this opportunity to say thank you to both of my
supervisors, Amanda Clare and Maria Liakata, for giving up so much of their
time to support me in designing and developing this project.

@@

Finally, I am eternally grateful for the support of my family and friends who
have put up with my gripes and moans throughout the duration of this project
and without whom, I may have given up hope on my dissertation.

@@

\chapter{Testing}
\input{testing}

>>>>

\usepackage{fullpage}
\usepackage{pdfpages}
%use the listings package
\usepackage{listings}
%use the English language
\usepackage[english]{babel}
%use graphics
\usepackage{graphicx}
%use wrap figures
\usepackage{wrapfig}
%geometry stuffs
\usepackage{lscape}
%use captions
\usepackage{caption}
%use multi-row tables
\usepackage{multirow}
\usepackage{url}
\usepackage{breakurl}
\usepackage{subcaption}
\usepackage{rotating}
\usepackage{pdflscape}

@@

I would like to take this opportunity to thank both of my
supervisors, Amanda Clare and Maria Liakata, for giving up so much of their
time to support me in designing and developing this project.

@@

Finally, I am eternally grateful for the support of my family and friends who
have put up with my gripes and moans throughout the duration of this project
and, without whom, I couldn't have achieved such an ambitious project.

@@

\chapter{Testing}
\label{chapter:testing}
\input{testing}
